Listening Effort MSC Analysis

### 2024-02-12 MSC 2024 Analysis/msc_analysis.Rmd
created data viz and perceived listening effort analysis

>>>>

rm(speaker_acc)

# Perceived Listening Effort

## Descriptives

perceived_effort_df <- data |>
  dplyr::select(subject, trial, speaker, effort_rating, rep_acc, code, trial_c) |>
  dplyr::distinct() |>
  # recoding missing effort ratings (negative effort ratings indicate missing data)
  dplyr::mutate(effort_rating = ifelse(effort_rating < 0, NA, effort_rating))

perceived_effort_df |>
  dplyr::select(speaker, effort_rating, rep_acc) |>
  tbl_strata(
    strata = rep_acc,
    ~.x |>
      tbl_summary(
        by = speaker,
        type = list(effort_rating ~ "continuous"),
        statistic = list(all_continuous() ~ c("{mean} ({sd})")),
        missing = "no",
        digits = all_continuous() ~ 2,
        label = list(effort_rating ~ "Perceived Listening Effort")
      ))

## Visualization

# Creating Custom Color Palette for Figures
library(NatParksPalettes) # install.packages("NatParksPalettes")
my_pal <- natparks.pals("Glacier", type = "discrete")

# Getting Sum stats for perceived effort

per_effort_des <- perceived_effort_df |>
  dplyr::group_by(speaker, rep_acc) |>
  dplyr::summarize(per_effort = mean(effort_rating, na.rm = T), 
                   sd = sd(effort_rating, na.rm = T),
                   se = sd/sqrt(n()))

# Plotting the mean perceived effort ratings for the ALS and control speaker
per_effort_des |>
  ggplot() +
   aes(x = rep_acc,
       y = per_effort,
       group = speaker,
       color = speaker,
       fill = speaker) +
  geom_bar(stat = "identity", alpha = 0.6, position = position_dodge()) +
  geom_errorbar(aes(ymin = per_effort - se, ymax = per_effort + se), width = 0.4, position = position_dodge(.9)) +
  labs(x = "Accuracy", y = "Perceived Listening Effort Rating") +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_color_manual(values = c(my_pal[1], my_pal[3])) +
  scale_fill_manual(values = c(my_pal[1], my_pal[3]))

# Saving the ggplot

ggsave("Plots/Perceived_effort.png", plot = last_plot(), height = 5, width = 5, units = "in")

## Perceived Listening Effort Models

### Fully Unconditional Model

m0 <- glmmTMB(effort_rating ~ 1 + (1|subject) + (1|code), data = perceived_effort_df)

sjPlot::tab_model(m0, pred.labels = "Intercept",
                  dv.labels = "Perceived Listening Effort")

performance::icc(m0)

```
### Model 1

m1 <- glmmTMB(effort_rating ~ 1 + (trial_c|subject) + (trial_c|code), 
           data = perceived_effort_df)

sjPlot::tab_model(m1, pred.labels = "Intercept",
                  dv.labels = "Perceived Listening Effort")

anova(m0, m1)

### Model 2

m2 <- glmmTMB(effort_rating ~ trial_c + (trial_c|subject) + (trial_c|code), 
              data = perceived_effort_df)

sjPlot::tab_model(m2, pred.labels = c("Intercept", "Trial Order"),
                  dv.labels = "Perceived Listening Effort")

anova(m1, m2)

```
### Model 3

m3 <- glmmTMB(effort_rating ~ trial_c + speaker + (trial_c|subject) + (trial_c|code), 
           data = perceived_effort_df)

sjPlot::tab_model(m3, pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]"),
                  dv.labels = "Perceived Listening Effort")

anova(m2, m3)

```
### Model 4

m4 <- glmmTMB(effort_rating ~ trial_c + speaker + rep_acc + (trial_c|subject) + (trial_c|code), 
           data = perceived_effort_df)

sjPlot::tab_model(m4, pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", "Phrase Repetition Accuracy [Inaccurate]"),
                  dv.labels = "Perceived Listening Effort")

anova(m3, m4)

```
### Model 5

m5 <- glmmTMB(effort_rating ~ trial_c + speaker + rep_acc + speaker*rep_acc + (trial_c|subject) + (trial_c|code), 
           data = perceived_effort_df)

sjPlot::tab_model(m5, pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", "Phrase Repetition Accuracy [Inaccurate]",
                                      "Speaker [ALS] * Phrase Repetition Accuracy [Inaccurate]"),
                  dv.labels = "Perceived Listening Effort")

anova(m4, m5)

```
### Model 6

m6 <- glmmTMB(effort_rating ~ trial_c + speaker + rep_acc + speaker*rep_acc + speaker*trial_c + (trial_c|subject) + (trial_c|code), 
           data = perceived_effort_df)

sjPlot::tab_model(m6, pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", "Phrase Repetition Accuracy [Inaccurate]",
                                      "Speaker [ALS] * Phrase Repetition Accuracy [Inaccurate]", "Speaker [ALS] * Trial Order"),
                  dv.labels = "Perceived Listening Effort")

anova(m5, m6)

### Model 7

m7 <- glmmTMB(effort_rating ~ trial_c + speaker + rep_acc + 
                speaker*rep_acc + speaker*trial_c + rep_acc*trial_c + (trial_c|subject) + (trial_c|code), 
           data = perceived_effort_df)

sjPlot::tab_model(m7, pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", "Phrase Repetition Accuracy [Inaccurate]",
                                      "Speaker [ALS] * Phrase Repetition Accuracy [Inaccurate]", "Speaker [ALS] * Trial Order",
                                      "Phrase Repetition Accuracy [Inaccurate] * Trial Order"),
                  dv.labels = "Perceived Listening Effort")

anova(m6, m7)

### Model 8

m8 <- glmmTMB(effort_rating ~ trial_c + speaker + rep_acc + 
                speaker*rep_acc + speaker*trial_c + rep_acc*trial_c + speaker*rep_acc*trial_c + (trial_c|subject) + (trial_c|code), 
           data = perceived_effort_df)

sjPlot::tab_model(m8, pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", "Phrase Repetition Accuracy [Inaccurate]",
                                      "Speaker [ALS] * Phrase Repetition Accuracy [Inaccurate]", "Speaker [ALS] * Trial Order",
                                      "Phrase Repetition Accuracy [Inaccurate] * Trial Order", 
                                      "Phrase Repetition Accuracy * Speaker * Trial Order"),
                  dv.labels = "Perceived Listening Effort",
                  file = "Tables/perceived_effort_model.html")

anova(m7, m8)

```{r, echo = F, message = F, warning = F}

rm(m0, m1, m2, m3, m4, m5, m6, m7, m8, per_effort_des)

# Pupil Dilation

## Preliminary Visualizations

Needing to spot any participants with odd trackings. Based on the visualizations below, LE13 and LE23 appear to have odd trackings, so they will be dropped from the current analyses.

```{r, warning = F, message = F}

data |>
  ggplot() +
  aes(x = time_norm,
      y = normed_pupil) +
  geom_smooth() +
  coord_cartesian(xlim = c(0,4908), ylim = c(-100, 200)) +
  facet_wrap("subject")

## Descriptives

### Getting Time Landmarks

```{r, message = F, warning = F}

data <- data |>
  dplyr::filter(subject != "LE13" & subject != "LE23")

data |>
  # Selecting relevant parameters
  dplyr::select(subject, trial, speaker, time_norm, code) |>
  # Filtering out times before phase onset
  dplyr::filter(time_norm >= 0) |>
  dplyr::group_by(speaker, code) |>
  dplyr::summarize(length = max(time_norm) - min(time_norm)) |>
  dplyr::ungroup() |>
  dplyr::summarize(av_length = mean(length),
                   av_phrase = av_length - 3000,
                   av_end_roi = av_length - 2000) %>%
  gt::gt() |>
  gt::cols_label(av_length = "Average Trial Length (ms)",
                 av_phrase = "Average Phrase Length (ms)",
                 av_end_roi = "Average Endpoint for ROI (ms)")

## Visualizations

```{r, warning = F, message = F}

data |>
  ggplot() +
  aes(x = time_norm,
      y = normed_pupil,
      group = speaker,
      color = speaker) +
  geom_smooth() +
  geom_vline(xintercept = 0, size = 0.35) +
  geom_vline(xintercept = 1910, linetype = 2) +
  annotate("rect", xmin = 500, xmax = 2910, ymin = -50, ymax = 200, alpha = 0.2) +
  coord_cartesian(xlim = c(0,4910), ylim = c(-100, 200)) +
  labs(x = "Normalized Time (ms)", y = "Pupil Dilation (arbitrary units)",
       caption = "Grey Box: Analysis Region of Interest \nSolid Line: Phrase Onset \nDotted Line: Phrase Offset") +
  facet_wrap("rep_acc") + 
  theme_bw() +
  scale_color_manual(values = c(my_pal[1], my_pal[3])) +
  theme(aspect.ratio = 1,
        plot.caption = element_text(hjust = 0))

ggsave("Plots/Pupil_dilation.png", plot = last_plot(), width = 10, height = 5, units = "in")
